\chapter{Personal Reflection}
This chapter's main purpose is to provide cross-critiques of the functioning of all members of the team.
These critiques will provide a means to reflect and improve during upcoming projects. 

\section{Affan Al Hakam}
I think all our members are good, improve the knowledge about the arduino codes to make it easy for next project.
that's it.
Because i think all of you are good, and the best team i have ever had.
\begin{description}
\item[Myself]
For this project, I think my contribution is more or less fine, and I always finished my project on time.
\item[Berend]
His communication is good to be a leader.
He organized the group nicely.
\item[Mohammed]
He is good in giving an idea, and he is finishing the project on time.
\item[Marwan]
He is creative to give an idea and he gives a decision about the number of segment we would use.
\end{description}

Lastly, for the next project, I expect every member should not delay the project, and take a responsible with what they are doing.

\section{Berend Al}
\begin{description}
\item[Myself]
I wasn't much help with soldering the hardware or building the box, most things I soldered, for example, had to be redone, but I think I well made up for it working the documentation and some of the code.

\item[Affan]
Affan appeared to me as a good engineer who knew their way around both hardware and software.
Affan didn't like to sit idle and whenever he was done with something he'd go look for something else on the projcect that needed work, which I found to be most respectable.
Contact with Affan was generally good, but because he didn't attend much of our lessons and lived a bit far away too there was a bit of a hurdle to discuss trivialities with him.

\item[Marwan]
Marwan was not very confident around writing software, but made marvellous functional designs and flowcharts, and had soldering skills far beyond the rest of us. 
Marwan has a keen eye for recognising the most practical solution, not just the most theoretically sound or the fastest short-term solution, this was of great use at several points during the project.
One thing that marwan didn't appear to fare as well in is with deadlines; There were a couple of occasions where his assigned tasks were slightly delayed.
I know there were some personal issues like he was moving into a new place, but it might be something to keep an eye on.

\item[Mohammed]
Mohammed seemed to be better at working with hardware than with software, but is quickly picking up the ropes on both fronts.
Mohammed partakes in this project great diligence, he puts effort into showing up on time, finishing work before deadlines and asks for help when needed.
He is someone who can get quite a lot of work done and someone you can rely on during the project.
Despite all this, Mohammed's work is sometimes found to bear mistakes, and I think he'd do good to practise a lot with digital systems and programming and learn how to test what works right and what doesn't.
\end{description}

\section{Marwan Al-Zadjali}
I don't have much remarks about my teammates, everyone was doing what was asked of them.

\section{Mohammed Musalhi}

\begin{description}
\item[Myself]
I think I cooperate well with the group members in every part,  to end up with a great result.
\item[Berend]
I think our leader Bernard was very active member, he tried to keep the work well organized using the project plan.
\item[Affan]
Affan as well was an active member, he have a good knowledge about the field.
\item[Marwar]
Marwan as well was a good member, he works hard especially with soldering the components and making the house.
\end{description}

In conclusion, this project helps me a lot to improve my functional skills and to have a brief knowledge about the major.

